\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{url}

\title{Reviewers}
\author{Pedro Ilídio, Felipe Kenji Nakano, Alireza Gharahighehi, \\ Ricardo Cerri and Celine Vens}
\date{December 2024}
\begin{document}
%
\maketitle

\begin{itemize}
\item Masashi Sugiyama: Professor at Department of Complexity Science and Engineering, Graduate School of Frontier Sciences, The University of Tokyo. Prof.dr. Sugiyama has authored numerous studies on related fields. He has also given many talks in the subject. More info available in his homepage: \url{http://www.ms.k.u-tokyo.ac.jp/sugi/index.html}    

\item Min-Ling Zhang:  Professor at School of Computer Science and Engineering in Southeast University, China. Prof.dr. Zhang has published a multitude of studies on machine learning problems with multi-outputs. More info available in his homepage: \url{https://palm.seu.edu.cn/zhangml/}     

\item Yu-Feng Li: Professor at National Key Laboratory for Novel Software Technology, Nanjing University, China. Prof.dr. Li has published multiple studies on weakly-supervised learning, a research field where the annotations are not reliable, similar to bipartite learning. More info available in his homepage: \url{https://cs.nju.edu.cn/liyf/}     

\item Isaac Triguero: Associate Professor of Data Science at the School of Computer Science of the University of Nottingham. Prof.dr. Triguero has published several works regarding semi-supervised learning, a research field that is investigates data with unrealiable annotations, similarly to bipartite learning.  More info available in his homepage: \url{https://people.cs.nott.ac.uk/pszit/}     

\end{itemize}
\end{document}
